\documentclass[11pt,a4paper,sans,english]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.85,top=1cm, a4paper]{geometry}
\usepackage{babel}
\usepackage{tikz}
\usepackage{pgfgantt}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\renewcommand*{\namefont}{\fontsize{38}{40}\mdseries\upshape}
\firstname{Mitchell}
\familyname{Hansen}                             % optional, remove/comment the line if not wanted
\address{9907 NE 124th ST}{Kirkland, WA}{USA}         % optional, remove/comment the line if not wanted; the "country" arguments can be omitted or provided empty
\mobile{509-607-0079}                          % optional, remove/comment the line if not wanted
\email{mitchellhansen0@gmail.com}                               % optional, remove/comment the line if not wanted
\homepage{mitchellhansen.info}                         % optional, remove/comment the line if not wanted
\extrainfo{\homepagesymbol\httplink{github.com/mitchellhansen}}
% \photo[64pt][0.4pt]{picture}                       % optional, uncomment the line if wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%


\begin{document}

%-----       resume       ---------------------------------------------------------

\makecvtitle
\vspace*{-8mm}

\section{Experience}
\cventry{Dec 2018 -- Present}{Embedded Software Developer}{CTR. Elektrobit, Protingent}{Bothell, WA}{}{
At Elektrobit I received training on the AUTOSAR automotive standards and Elektrobits related tooling. This has
been a much more embedded-first development experience as opposed to my linux-first experience developing for other products. 
At Elektrobit I was also given the chance to gain fantastic real world linux kernel and kernel module development experience on 
a large automotive linux project.
}

\cventry{July 2017 -- Dec 2018}{Software Developer (Embedded / Full Stack Web)}{Espial}{Kirkland, WA}{}{
At Espial I initially applied my knowledge of embedded products and C/C++ to hunt for bugs
in a legacy set-top-box C++ codebase. I also aided in maintenance of the test automation 
framework for said codebase. I later pivoted to another role in the cloud services team, in which we 
performed all the engineering required for maintaining and developing a large IPTV SaaS solution. This 
included bug fixes, feature work, automation (test\&build), releases, and if we were unlucky, cm and ops.
}

\cventry{June 2016 -- Sept. 2016}{Full Stack Web Developer, Intern}{Donuts Inc.}{Bellevue, WA}{}{
At Donuts I received a crash course in agile development and general software practices. I had up to this point
been a pure C/C++ programmer with occasional spats of C\#. Donuts operated on a HTML + python + Google Cloud stack
which was completely new for me, and forced me out of my comfort zone. I credit this for strengthening my ability to pivot
between languages, frameworks, and environments.
\newline
\newline
i.e I wrote a bunch of Google Cloud microservices and tools
}

\section{Education}
\cventry{2012--2017}{B.S. in Computer Science}{Central Washington University}{Ellensburg, WA}{}{}  % arguments 3 to 6 can be left empty
\cventry{Birth - Present}{Mega-Nerd}{}{}{}{I'm a lifelong learner and a total nerd. I program as a hobby, love learning new things, and am always up for a challenge.}
\section{Skills \& Languages}


\cventry{}{In depth knowledge / Professional experience}{}{}{}{
	C++, Java, Python, OpenCL, Linux, Git / Perforce
}

\cventry{}{Enough to be dangerous}{}{}{}{
	SQL, Javascript, HTML \& CSS, 3D Graphics, Android, AWS, Alexa, Bash, Clang \& GCC
}

\cventry{}{Passing knowledge, enough to sound dangerous}{}{}{}{
	AUTOSAR, AppEngine, Flask, SVN, GDB, \LaTeX, OpenGL, Unity3D, Windows \& Mac
}

\vspace*{-2mm}

\section{Portfolio}
\cventry{}{Volumetric Rendering Engine}{OpenCL, C++, SFML, Voxel Ray Marching, 3D Math}{}{}{
	An experimental "From Scratch" volumetric rendering engine utilizing a voxel dataset
	organized in a sparse voxel octree, Blinn-Phong lighting, dynamic shadowing, texturing,
	and reflections, along with a TCP streaming Android controller. Presented at the CWU
	College Of The Sciences fair.
}
\cventry{}{Conways Game of Life}{OpenCL, C++, SFML}{}{}{Completely in-core GPU Conways Game of Life simulator and accompanying RLE decoder.}
\cventry{}{Optimization Algorithms}{C++, Computer Science Mathematics}{}{}{Implementation of 15 optimization test suite functions, and 9 popular mathematical optimization algorithms.}
\cventry{}{Project Euler}{Python, Computer Science Mathematics}{}{}{Combinatorics, discrete math, and other logic problems solved using Python.}
\end{document}
